### 2020-01-31 wuhan.tex
spelling

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As epidemic progresses, many disease modelers have prioritized their attention to estimating the basic reproductive number \Ro, which is defined as the average number of secondary cases caused by a primary case.
While their efforts are extremely valuable, their modeling approaches and, inevitably, their estimates vary widely.
Here, we present a novel framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to arly estimates of \Ro\ for the 2019-nCoV outbreak.
Our results demonstrate the importance of propagating uncertainties in all three quantities, in particular in the mean generation interval.
We recommend that more efforts should be

@@

Early in an outbreak, \Ro is difficult to estimate directly;
instead, \Ro is often inferred from the exponential growth rate $r$, which can be estimated reliably from incidence data \citep{mills2004transmissibility, nishiura2009transmission, ma2014estimating}.
Given an estimate of the exponential growth rate $r$ and an \emph{instrinsic} generation-interval distribution $g(\tau)$ \citep{champredon2015intrinsic}, the basic reproductive
number can be estimated via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{linenomath*}
\begin{equation}
1/\mathcal R_0 = \int \exp(-r\tau) g(\tau) d\tau.
\label{eq:euler}
\end{equation}
\end{linenomath*}
In other words, estimates of \Ro must
depend on the assumptions about the
exponential growth rate $r$ and the shape of the generation-interval distribution $g(\tau)$.

>>>>

\section*{Abstract}
A novel coronavirus (2019-nCoV) has recently emerged as a global threat. 
As epidemic progresses, many disease modelers have prioritized their attention to estimating the basic reproductive number \Ro, which is defined as the average number of secondary cases caused by a primary case.
While their efforts are extremely valuable, their modeling approaches and, inevitably, their estimates vary widely.
Here, we present a novel framework for comparing different estimates of \Ro\ across a wide range of models by decomposing it into three key quantities (the exponential growth rate $r$, the mean generation interval $\bar G$, and the generation-interval dispersion $\kappa$) and apply our framework to early estimates of \Ro\ for the 2019-nCoV outbreak.
Our results demonstrate the importance of propagating uncertainties in all three quantities, in particular in the mean generation interval.
We recommend that more efforts should be

@@

Early in an outbreak, \Ro is difficult to estimate directly;
instead, \Ro is often inferred from the exponential growth rate $r$, which can be estimated reliably from incidence data \citep{mills2004transmissibility, nishiura2009transmission, ma2014estimating}.
Given an estimate of the exponential growth rate $r$ and an \emph{intrinsic} generation-interval distribution $g(\tau)$ \citep{champredon2015intrinsic}, the basic reproductive
number can be estimated via the Euler-Lotka equation \citep{wallinga2007generation}:
\begin{linenomath*}
\begin{equation}
1/\mathcal R_0 = \int \exp(-r\tau) g(\tau) d\tau.
\label{eq:euler}
\end{equation}
\end{linenomath*}
In other words, estimates of \Ro must
depend on the assumptions about the
exponential growth rate $r$ and the shape of the generation-interval distribution $g(\tau)$.
